\cvsection{Work Experience}
\begin{cventries}
\cventry
{Undergraduate Research Assistant}
{University of Guelph}
{Guelph, ON}
{2022}
{
\begin{cvitems}
\item {Worked under Dr. Stacey Scott to review and summarize academic publications relating precision agriculture and computer vision.}
\item {Self-directed research of contemporary neural network concepts and methods.}
\item {Exploration of Mask-RCNN, YOLO, detectron2 API networks.}
\item {Used PyTorch and OpenCV to train a residual neural network to classify cattle in frames of video to support concurrent agriculture research.}
\end{cvitems}
}\cventry
{Rock Climbing Monitor}
{University of Guelph Athletic Centre}
{Guelph, ON}
{2022/2023}
{
\begin{cvitems}
\item {Helped build and maintain a thriving community of climbing enthusiasts on campus.}
\item {Interacted personally with patrons and provided quality service to members}
\item {Facilitated orientations, “Learn to Climb” sessions, first aid support, taught belay certification.}
\item {Managed sale of rock climbing equipment and assessed needs of customers.}
\end{cvitems}
}\cventry
{Outdoor Educator}
{Kandalore Outdoor Education Centre}
{Kawartha Highlands, ON}
{2023}
{
\begin{cvitems}
\item {Lead school groups grades 6 to 11 in educational and team-building activities as a group leader.}
\item {Interacted with teachers to ensure quality leadership for their students during their time at Kandalore.}
\item {Facilitated technical activities including indoor and outdoor rock climbing, high ropes course, map orienteering, etc.}
\item {Worked with dedicated staff team to maintain a functioning site including a variety of manual labour and maintenance tasks.}
\end{cvitems}
}\cventry
{Camp Counselor/River Guide}
{Camp Kandalore}
{Kawartha Highlands, ON}
{2019/2021}
{
\begin{cvitems}
\item {Facilitated camp activities including ORCA canoe progression, nature walks, sailing as well as assigned-cabin activities.}
\item {Planned and organized 3-to-7-day white-water and flat-water wilderness canoe camping trips for groups of 8 to 10 campers.}
\item {Worked with staff to ensure safe environments for learning and adventure. Promoted clean and sustainable camping practices.}
\item {Monitored group dynamics and encouraged growth of teamwork and communication skills among campers.}
\item {Maintained a clean environment in-camp including boat repair and site maintenance.}
\end{cvitems}
}\cventry
{Cook}
{Stampede Ranch}
{Guelph, ON}
{2020}
{
\begin{cvitems}
\item {Worked in a fast-paced high-pressure environment to ensure timely delivery of quality prepared food.}
\item {Maintained a clean and organized work environment including closing procedures.}
\item {Worked with other staff in team environment to maintain efficient work environment.}
\end{cvitems}
}
\end{cventries}