\cvsection{Projects}
\begin{cventries}
\cventry
{Full-stack serviced webpage delivering detailed information about prerequisites, course searching, program informaition using web-scraped university data, built on React.}
{Program Planner Website}
{}
{2022}
{
\begin{cvitems}
\item {Used AGILE methodology in a team setting to ensure effective software development as a team leader across multiple sprints}
\item {Built user-friendly front end application using React, React Flow and other libraries, Bootstrap, and Javascript.}
\item {Organized weekly requirements, scheduled team meetings, lead code review sessions}
\item {Used Flask, NGINX, Python for backend development on a Linux server.}
\end{cvitems}
}\cventry
{Took part in designing a social media app for a local community partner.}
{The Grove Youth Wellness Hubs App Design}
{}
{2021}
{
\begin{cvitems}
\item {Communicated with client to assemble requirements and key features for a social media app.}
\item {Involed Waterfall design methodology to build a development plan, collaborated with team members on requirements and UI design.}
\end{cvitems}
}\cventry
{Evaluation and analysis of Moose Habitat sustainability in the Missinaibi Forest}
{Moose Habitat Suitability Modelling in Northern Ontario}
{}
{2023}
{
\begin{cvitems}
\item {Collaborated with students and graduate to identify areas of concern, research plan.}
\item {Performed a detailed literature review of moose habitat suitability and environmental concerns related to indstrial logging, including government policy and forestry guidelines.}
\item {Investaged and prepared vector data provided through government resources and forestry for analysis.}
\item {Derived raster layers and relevant information and developed a Habitat suitability model using ArcGIS pro.}
\end{cvitems}
}\cventry
{Independently produced feature length film.}
{Ant - Director of Photography, Producer}
{}
{2024}
{
\begin{cvitems}
\item {Helped plan and execute shooting locations, storyboards, direction, lighting, sound and videography}
\item {Operated camera and audio equipment on set.}
\item {Worked closely with director and actors to ensure smooth and efficient shoot days.}
\item {Intimately involved in pre and post-production processes.}
\end{cvitems}
}\cventry
{Composed, recordered, and produced soundtrack for independent student short horror film.}
{Sole of a Salesman - Composer}
{}
{2022}
{
\begin{cvitems}
\item {Wrote, recorded, and produced music using digital tools and real instruments.}
\item {Worked closely with director to match tone of film and assess needs.}
\end{cvitems}
}
\end{cventries}